Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-16 VMCAI-revised-version/final.tex
up

\alain{le rappel ci-dessous est-il entièrement utile ? Je pense qu'on peut l'enlever, et toi ?}
Now, we may recall a simple condition that insures that a finite basis of $\pred^*(\uparrow s )$ is computable for every $s \in S$.
We will use the following property: if $\mathscr{S}$ is a WSTS with strong compatibility and $U \subseteq S$ is upward-closed, then $\pred(U )$, $\pred^k(U )$ with $k\geq0$, and $\pred^*(U )$ are all upward-closed \cite{DBLP:journals/tcs/FinkelS01}.
For a WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ and an upward-closed set $U  \subseteq S$, let us study the convergence of the sequence defined by $U_0=U$ and $U_k= U_{k-1} \cup \pred(U_{k-1})$ for $k \geq 1$. When $\mathscr{S}$ has strong compatibility, the sets $U_k$ are upward-closed and $U_k \subseteq U_{k+1}$ so we know that the sequence $(U_k)_k$ converges. Let us define the \emph{index} of convergence of the sequence $U_k$ as the smallest $k_0$ s.t. $U_k = U_{k_0}$ for all $k \geq k_0$. We may compute $k_0$ and we then have:  $\pred^*(U) = U_{k_0}$. When $\mathscr{S}$ have upward-compatibility but not strong compatibility, we can similarly compute $\pred^*(U)$ by studying the sequence $(\uparrow U_k)_k$ instead.
With the effective pred-basis hypothesis, we obtain:

\begin{theorem}\cite{DBLP:journals/tcs/FinkelS01,DBLP:journals/iandc/AbdullaCJT00}
A finite basis of $ \pred^*(U)$ is computable for any effective WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ with effective pred-basis and any upward-closed set $U \subseteq S$ given with its finite basis $B_U$. Hence coverability is decidable.
\end{theorem}

Let us recall that a Well Behaved Transition System (WBTS) \cite{DBLP:journals/lmcs/BlondinFM17} is an upward compatible ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ where $(S,\leq)$ that contains no infinite antichains (but it can be not well founded). The class of WBTS is strictly larger than WSTS: for example, integer VASS under the lexicographical ordering are WBTS but not WSTS \cite{DBLP:journals/lmcs/BlondinFM17}. 
With the ideally-effective hypothesis, we obtain the decidability of coverability for WBTS (without the effective pred-basis hypothesis).

\begin{theorem}\cite{DBLP:journals/lmcs/BlondinFM17}
Coverability is decidable for any ideally-effective WBTS.
\end{theorem}

>>>>

\alain{le rappel ci-dessous est-il entièrement utile ? Je pense qu'on peut l'enlever, et toi ?}
Now, we may recall a simple condition that insures that a finite basis of $\pred^*(\uparrow s )$ is computable for every $s \in S$.
We will use the following property: if $\mathscr{S}$ is a WSTS with strong compatibility and $U \subseteq S$ is upward-closed, then $\pred(U )$, $\pred^k(U )$ with $k\geq0$, and $\pred^*(U )$ are all upward-closed \cite{DBLP:journals/tcs/FinkelS01}.
For a WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ and an upward-closed set $U  \subseteq S$, let us study the convergence of the sequence defined by $U_0=U$ and $U_k= U_{k-1} \cup \pred(U_{k-1})$ for $k \geq 1$. When $\mathscr{S}$ has strong compatibility, the sets $U_k$ are upward-closed and $U_k \subseteq U_{k+1}$ so we know that the sequence $(U_k)_k$ converges. Let us define the \emph{index} of convergence of the sequence $U_k$ as the smallest $k_0$ s.t. $U_k = U_{k_0}$ for all $k \geq k_0$. We may compute $k_0$ and we then have:  $\pred^*(U) = U_{k_0}$. When $\mathscr{S}$ have upward-compatibility but not strong compatibility, we can similarly compute $\pred^*(U)$ by studying the sequence $(\uparrow U_k)_k$ instead.
With the effective pred-basis hypothesis, we obtain:\\

\noindent
\textbf{Theorem.}
{\em ~\cite{DBLP:journals/tcs/FinkelS01,DBLP:journals/iandc/AbdullaCJT00}
 A finite basis of $ \pred^*(U)$ is computable for any effective WSTS $\mathscr{S}=(S, \rightarrow, \leq)$ with effective pred-basis and any upward-closed set $U \subseteq S$ given with its finite basis $B_U$. Hence coverability is decidable.
}\\

Let us recall that a Well Behaved Transition System (WBTS) \cite{DBLP:journals/lmcs/BlondinFM17} is an upward compatible ordered transition system $\mathscr{S}=(S, \rightarrow, \leq)$ where $(S,\leq)$ that contains no infinite antichains (but it can be not well founded). The class of WBTS is strictly larger than WSTS: for example, integer VASS under the lexicographical ordering are WBTS but not WSTS \cite{DBLP:journals/lmcs/BlondinFM17}. 
With the ideally-effective hypothesis, we obtain the decidability of coverability for WBTS (without the effective pred-basis hypothesis).\\

\noindent
\textbf{Theorem.}
{\em ~\cite{DBLP:journals/lmcs/BlondinFM17}
Coverability is decidable for any ideally-effective WBTS.
}\\
